---
title: "Linear_Model_Prediction"
author: "Peter Dang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(knitr)
data<-read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt", sep="",header=TRUE)

```


### Model1: SIMS~ARM

```{r}
basiccNN<- ggplot(data,aes(y=SIMS,x=ARM)) 
```

```{r}
basiccNN +geom_point() +ggtitle("SIMS vs ARM") 
```

We have a scatterplot for SIMS vs ARM and it seems that the plot is going up to the right. 






### Numerical Results 
```{r}
cor(SIMS~ARM,data=data)
```

### Inferential Results 
```{r}
model1<-lm(SIMS~ARM,data=data)
summary.lm(model1)
```








### Target Dataframe 

```{r}
target<-data.frame(ARM=90,GRIP=90)
```

```{r}
predict(model1,target,interval=c("prediction"))
```

```{r}
predict(model1,target,interval=c("confidence"))
```

```{r}
armmod <- lm(SIMS~ARM,data=data)
plot(SIMS~ARM,data=data)
abline(armmod)
summary.lm(armmod)
```





### Model2 SIMS~GRIP 
```{r}
basiccNN2<- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basiccNN2 +geom_point() +ggtitle("SIMS vs GRIP")
```

The relationship is a positive relationship, as the plot is going up to the right. 

### Numerical Results 2 
```{r}
cor(SIMS~GRIP,data=data)
```

The correlation between SIMS and GRIP is less than the correlation between SIMS and ARM. 


### Inferential Results 2
```{r}
model2<-lm(SIMS~GRIP,data=data)
summary.lm(model2)
```

The adjusted R squared for SIMS vs ARM is bigger than SIMS vs GRIP. 

```{r}
gripmod <- lm(SIMS~GRIP,data=data)
plot(SIMS~GRIP,data=data)
abline(gripmod)
summary.lm(gripmod)
```
