---
title: "Linear_Model_Prediction"
author: "Peter Dang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(knitr)
data<-read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt", sep="",header=TRUE)

```


### Model1: SIMS~ARM

```{r}
basiccNN<- ggplot(data,aes(y=SIMS,x=ARM)) 
```

```{r}
basiccNN +geom_point() +ggtitle("SIMS vs ARM") 
```

We have a scatterplot for SIMS vs ARM and it seems that the plot is going up to the right. 






### Numerical Results 
```{r}
cor(SIMS~ARM,data=data)
```

### Inferential Results 
```{r}
model1<-lm(SIMS~ARM,data=data)
summary.lm(model1)
```








### Target Dataframe 

```{r}
target<-data.frame(ARM=90,GRIP=90)
```

```{r}
predict(model1,target,interval=c("prediction"))
```

```{r}
predict(model1,target,interval=c("confidence"))
```

### Linear fit Model 1

```{r}
basiccNN +geom_point() +ggtitle("SIMS vs ARM") +geom_smooth(method=lm)
```









### Model2 SIMS~GRIP 
```{r}
basiccNN2<- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basiccNN2 +geom_point() +ggtitle("SIMS vs GRIP") 
```

The relationship is a positive relationship, as the plot is going up to the right. 

### Numerical Results 2 
```{r}
cor(SIMS~GRIP,data=data)
```

The correlation between SIMS and GRIP is less than the correlation between SIMS and ARM. 


### Inferential Results 2
```{r}
model2<-lm(SIMS~GRIP,data=data)
summary.lm(model2)
```

The adjusted R squared for SIMS vs ARM is bigger than SIMS vs GRIP. 

```{r}
basiccNN2 +geom_point() +ggtitle("SIMS vs GRIP") +geom_smooth(method=lm)
```


### Model3 SIMS~ARM+GRIP


```{r}
cor(SIMS~ARM,data=data)
cor(SIMS~GRIP,data=data)
cor(SIMS~ARM+GRIP,data=data)
```


### Inferential results Model3 

```{r}
model3=lm(SIMS~ARM+GRIP,data=data)
summary.lm(model3)
```

OUR equation is SIMS= -5.43387 +0.03731*ARM +0.02447*GRIP. That is the line in 3D space. 
